Two-Dimensional Hydrodynamics of a Janus Particle Vesicle

### 2022-03-27 doc/JFM2022/Final/main_jfm.tex
figure color and text mods

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{fig1.eps}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution 
  $\eta$ of \eqref{eq:SL}. Red is for $\eta  = 1$ and blue is for $\eta  = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve and $A$ is the enclosed area.
  %, and $L$ is the arc length. 
  Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=11cm]{fig4a.eps}\\
  \includegraphics[width=11cm]{fig4b.eps}
\end{center} 
\caption{\label{figure5} Inter-monolayer slip is present in the JP
  vesicle tank-treading motion at all shear rates. Panel (a) tracks a
  pair of particles (blue and yellow). The shear rate is $\chi=0.005$
  and in the right figure, the yellow particle will complete two and a
  quarter revolutions in the same time the blue particle completes two
  revolutions. The curves in panel (b) are the distance the outer
  leaflet has slid past the inner leaflet. The slopes of the curves
  give the slip velocity. 
  Slip velocity is generally monotonic in the shear rate.
  The case $\chi = 0.003$ is an exception.}
\end{figure}

Figure~\ref{figure3} shows snapshots of the JP vesicle in the shear flow
with $\chi=0.0025$. Under the background flow, the rigid-body boundary
condition~\eqref{eq:rigid_bc} causes the particle suspension to
elongate. This perturbation disrupts the preferred particle orientations
and exposes the hydrophobic core to bulk water (Figure~\ref{figure3},
red region). In response, hydrophobic
attraction~\eqref{eq:hydrophobicAttraction} causes the particles to
reorient and form a somewhat elliptically-shaped suspension. Panel (a)
shows the initial configuration and panel (b) shows the later,
fully-formed, clockwise tank-treading motion. The JP suspension
maintains its bilayer structure throughout the simulation. 
(See Supplementary Movie S2 for tank-treading vesicle with $\chi=0.005$.)
%

@@

Figure~\ref{figure5}a illustrates inter-monolayer slip by tracking the distances
traveled by a pair of particles along the midplane curve. In the left image, the blue and yellow
particle lie next to each other. In the right-most panel, the yellow
particle has traveled farther than the blue particle. This suggests that
the outer tangential velocity, obtained by projecting the velocity of the
outer leaflet onto the midplane curve, 
is larger than that of the inner leaflet 
(see Supplementary Movie S3).

@@

An empirical numerical study found that for the baseline
parameter set, the dimensionless, critical shear rate is $\chi_*=0.0655$
so that the membrane ruptured whenever $\chi > \chi_*$ and did not
rupture whenever $\chi < \chi_*.$ Supplementary Materials Movie 4 shows
the membrane rupture at the critical shear rate.  To further quantify
the competition between shear and attraction, we found that a $5 \%$
relative increase in the parameters $\gamma$ and $M$ resulted in a $4.24
\%$ relative increase in $\chi_*$, from $0.0655$ to $0.0688$.  A $5 \%$
decrease in the particle radius $c$, screening length $\rho$ gave a
$-9.55 \%$ decrease, $5.0 \%$ increase respectively in $\chi_*$.
Finally, a $10 \%$ increase in resting length $L_0$ gave a $20.61 \%$
decrease in critical shear rate $\chi_*$.  
These relative changes suggest that there is dimensionless number $K$ given by 
  \begin{equation}
    \label{eq:CSR}
  \mu \dot\gamma_* = K \frac{\gamma c^2}{\rho L^2}
  \end{equation}
  that relates hydrophobic attraction to the dimensional critical shear rate $\dot \gamma_* = \chi_* \text{ ns}^{-1}$.
  Assuming a characteristic velocity $L\dot \gamma_*$, the number $K$ relates to the vesicle's capillary number
  $\text{Ca} = K c^2/(\rho L)$. Based on the above data, $\text{Ca}$ would be approximately $1.8$
  so that surface forces are comparable to viscous forces.  
  There is a related \emph{elastic} capillary number
  $\widetilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/K_B$
  used to characterize rheological properties of lipid bilayer membranes
  where $R_0$ is vesicle radius $K_B$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
  Setting $\text{Ca}$ and $\widetilde{\text{Ca}}$ equal, we can derive
  \[
  K_B = \frac{\mu \dot \gamma_* R_0^3}{\text{Ca}}
  \]
  which yields $K_B \approx 100$ pN $\text{nm}$, which is a large
  value for the bending modulus of a reasonable lipid bilayer given the many assumptions and approximations \citep{NaTr00}.

@@

Figure~\ref{figure6} shows four configurations for one specific case
where the centroid of the JP vesicle is initially placed slightly above
the $x$-axis. We have marked a pair of particles blue and yellow in the
inner and outer leaflets, respectively, and observe that the deformed JP
vesicle (Figure~\ref{figure6}, $t = 12~\upmu$s) has a counterclockwise
movement and the shape of the vesicle approaches an asymmetric slipper
shape. For this test, the reduced area in the final configuration is
approximately $0.9$ which matches the previous numerical tests
in~\cite{Kaoui09} where a slipper-like shape occurs when the flow
velocity is weak and the reduced area is large. The flow causes the
vesicle, which is initially placed above the axis, to drift downward
where it reaches a steady height of about $1$ nm.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig8.eps}
\caption{\label{figure2}  
The ratios of the abscissa and ordinates from Figure \ref{figure2part1}c, d are well-fit by constant functions (baseline, dots).
The open circles and diamonds are for $\gamma$ and $M$ increased by 5$\%$ and 10$\%$, respectively. 
The x's and stars are for particle radius, $\rho$, and $\rho_0$ decreased by 5$\%$ and 10$\%$, respectively.
The variable $x$ is used to denote the horizontal axis coordinate. 
}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{fig1.eps}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution 
  $\eta$ of \eqref{eq:SL}. Magenta is for $\eta  = 1$ and turquoise is for $\eta  = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve and $A$ is the enclosed area.
  %, and $L$ is the arc length. 
  Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=11cm]{fig4a.eps}\\
  \includegraphics[width=11cm]{fig4b.eps}
\end{center} 
\caption{\label{figure5} Inter-monolayer slip is present in the JP
  vesicle tank-treading motion at all shear rates. Panel (a) tracks a
  pair of particles (filled circles). The shear rate is $\chi=0.005$
  and in the right figure, the particle in the outer monolayer will complete two and a
  quarter revolutions in the same time the particle in the inner monolayer completes two
  revolutions. The curves in panel (b) are the distance the outer
  leaflet has slid past the inner leaflet. The slopes of the curves
  give the slip velocity. 
  Slip velocity is generally monotonic in the shear rate.
  The case $\chi = 0.003$ is an exception.}
\end{figure}

Figure~\ref{figure3} shows snapshots of the JP vesicle in the shear flow
with $\chi=0.0025$. Under the background flow, the rigid-body boundary
condition~\eqref{eq:rigid_bc} causes the particle suspension to
elongate. This perturbation disrupts the preferred particle orientations
and exposes the hydrophobic core to bulk water (Figure~\ref{figure3},
magenta region). In response, hydrophobic
attraction~\eqref{eq:hydrophobicAttraction} causes the particles to
reorient and form a somewhat elliptically-shaped suspension. Panel (a)
shows the initial configuration and panel (b) shows the later,
fully-formed, clockwise tank-treading motion. The JP suspension
maintains its bilayer structure throughout the simulation. 
(See Supplementary Movie S2 for tank-treading vesicle with $\chi=0.005$.)
%

@@

Figure~\ref{figure5}a illustrates inter-monolayer slip by tracking the distances
traveled by a pair of particles along the midplane curve. In the left image,
two particles indicated by filled circles lie next to each other. In the right-most panel, the
particle in the outer monolayer has traveled farther than the
particle in the inner monolayer. This suggests that
the outer tangential velocity, obtained by projecting the velocity of the
outer leaflet onto the midplane curve, 
is larger than that of the inner leaflet 
(see Supplementary Movie S3).

@@

An empirical numerical study found that for the baseline
parameter set, the dimensionless, critical shear rate is $\chi_*=0.0655$
so that the membrane ruptured whenever $\chi > \chi_*$ and did not
rupture whenever $\chi < \chi_*.$ Supplementary Materials Movie 4 shows
the membrane rupture at the critical shear rate.  To further quantify
the competition between shear and attraction, we found that a $5 \%$
relative increase in the parameters $\gamma$ and $M$ resulted in a $4.24
\%$ relative increase in $\chi_*$, from $0.0655$ to $0.0688$.  A $5 \%$
decrease in the particle radius $c$, screening length $\rho$ gave a
$-9.55 \%$ decrease, $5.0 \%$ increase respectively in $\chi_*$.
Finally, a $10 \%$ increase in resting length $L_0$ gave a $20.61 \%$
decrease in critical shear rate $\chi_*$.  
These relative changes suggest that there is dimensionless number $K$ given by 
  \begin{equation}
    \label{eq:CSR}
  \mu \dot\gamma_* = K \frac{\gamma c^2}{\rho L^2}
  \end{equation}
  that relates hydrophobic attraction to the dimensional critical shear rate $\dot \gamma_* = \chi_* \text{ ns}^{-1}$.
  Assuming a characteristic velocity $L\dot \gamma_*$, the number $K$ relates to the vesicle's capillary number
  $\text{Ca} = K c^2/(\rho L)$. Based on the above data, $\text{Ca}$ would be approximately $1.8$
  so that surface forces are comparable to viscous forces.  
  There is a related \emph{elastic} capillary number
  $\widetilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/K_B$
  used to characterize rheological properties of lipid bilayer membranes
  where $R_0$ is vesicle radius $K_B$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
  Setting $\text{Ca}$ and $\widetilde{\text{Ca}}$ equal, we can derive
  \[
  K_B = \frac{\mu \dot \gamma_* R_0^3}{\text{Ca}}
  \]
  which yields $K_B \approx 100$ pN $\text{nm}$.
  Albeit somewhat large, the resulting bending modulus is
  reasonable considering the assumptions made.

@@

Figure~\ref{figure6} shows four configurations for one specific case
where the centroid of the JP vesicle is initially placed slightly above
the $x$-axis. We have marked a pair of particles (filled circles) in the
inner and outer leaflets, respectively, and observe that the deformed JP
vesicle (Figure~\ref{figure6}, $t = 12~\upmu$s) has a counterclockwise
movement and the shape of the vesicle approaches an asymmetric slipper
shape. For this test, the reduced area in the final configuration is
approximately $0.9$ which matches the previous numerical tests
in~\cite{Kaoui09} where a slipper-like shape occurs when the flow
velocity is weak and the reduced area is large. The flow causes the
vesicle, which is initially placed above the axis, to drift downward
where it reaches a steady height of about $1$ nm.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig8.eps}
\caption{\label{figure2}  
The ratios of the abscissa and ordinates from Figure \ref{figure2part1}c, d are well-fit by constant functions (baseline, dots).
The open circles and diamonds are for $\gamma$ and $M$ increased by 5$\%$ and 10$\%$, respectively. 
The exes and stars are for particle radius, $\rho$, and $\rho_0$ decreased by 5$\%$ and 10$\%$, respectively.
The variable $x$ is used to denote the horizontal axis coordinate. 
}
\end{figure}
